---
title: "Diagnostic Plots"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
# Repeated Sprint Ability Models
## Disability Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_disability_rsa_model)

rhat_plot_disability_rsa_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_disability_rsa_model)

trace_plot_disability_rsa_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_disability_rsa_model)

pp_check_disability_rsa_model

```

## Classification Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_classif_rsa_model)

rhat_plot_classif_rsa_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_classif_rsa_model)

trace_plot_classif_rsa_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_classif_rsa_model)

pp_check_classif_rsa_model

```

# Sprint Velocity Models
## Disability Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_disability_velocity_model)

rhat_plot_disability_velocity_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_disability_velocity_model)

trace_plot_disability_velocity_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_disability_velocity_model)

pp_check_disability_velocity_model

```

## Classification Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_classif_velocity_model)

rhat_plot_classif_velocity_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_classif_velocity_model)

trace_plot_classif_velocity_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_classif_velocity_model)

pp_check_classif_velocity_model

```

# Sprint Acceleration Models
## Disability Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_disability_acceleration_model)

rhat_plot_disability_acceleration_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_disability_acceleration_model)

trace_plot_disability_acceleration_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_disability_acceleration_model)

pp_check_disability_acceleration_model

```

## Classification Models
### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_plot_classif_acceleration_model)

rhat_plot_classif_acceleration_model 


```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_classif_acceleration_model)

trace_plot_classif_acceleration_model

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_classif_acceleration_model)

pp_check_classif_acceleration_model

```
