---
title: "Statistical Analysis and Results"
format: 
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    prefer-html: true
bibliography: references.bib
csl: apa.csl
---

```{r} 
#| message: false
#| warning: false
#| echo: false
#| include: false


knitr::opts_chunk$set(echo = TRUE, fig.align="center")
options(knitr.kable.NA = '')

library(tidyverse)
library(kableExtra)
library(ggtext)
library(patchwork)

```

# Statistical Analysis

The present analysis was not pre-registered as we had no a priori hypotheses and, given the limited sample size due to resource constraints and the population, thus was considered exploratory. Inferential statistics were treated as highly unstable local descriptions of the relations between model assumptions and data in order to acknowledge the inherent uncertainty in drawing generalised inferences from single and small samples [@amrhein_inferential_2019]. For all analyses we opted to avoid dichotomising the existence of effects and therefore did not employ traditional null hypothesis significance testing on parameter estimates [@amrhein_scientists_2019; @mcshane_abandon_2019]. Instead, we opted to take an estimation-based approach instead [@cumming_new_2014], based within a Bayesian framework [@kruschke_bayesian_2018]. For all analyses model parameter estimates and their precision, along with conclusions based upon them, were interpreted continuously and probabilistically, considering data quality, plausibility of effect, and previous literature, all within the context of each model. We focused primarily on qualitative examination of our results based on visualization of the data and models for fixed effects, and exploration of variances using random effects. All analysis was performed in R (version 4.2.3, The R Foundation for Statistical Computing, 2023) and all data and code is presented in the supplementary materials (https://osf.io/y2jdb/). Two sets of models were employed exploring the sprint trial outcomes, and the repeated sprint outcomes, for both classification (4 vs 5) and disability (other vs SCI). The `brms` package [@burkner_brms_2017] was used to fit all models. All parameters in the models described below had $\hat{R}$ values $\leq{1.01}$, trace plots demonstrated chain convergence, and the posterior predictive checks appeared appropriate (see https://osf.io/juex5). Given population and outcomes explored, the limited data available in past studies, and the model structures, we did not have a clear intuition or informed opinion about what priors to set and so opted to use the default weakly regularising priors and "let the data speak". Four Monte Carlo Markov Chains with 4000 warmup and 4000 sampling iterations were used in each model. For each model results were visualised by taking draws from the expected posterior distribution (n=16000) and taking the mean of these draws along with the 95% quantile (credible) interval for the fixed effects parameters, thus providing the overall grand mean effects for the population. All data visualisations were made using `ggplot2` [@wickham_ggplot2_2022], the `tidybayes` package [@kay_tidybayes_2022], and the `patchwork` package [@pedersen_patchwork_2022].

## Sprint trial outcomes

For the sprint trials we examined both the velocities and accelerations over each of the 5m sections of the 20m sprint as dependent variables in separate models. Data was handled in long format with each row corresponding to an observation of a participants velocity or acceleration in a 5m section for a given trial. For each of velocity and acceleration we fit separate models with fixed effects for either disability or classification, and in each also included a fixed effect for the distance (i.e., section of the 20m sprint trial: 0-5m, 5-10m, 10-15m, 15-20m), in addition to their interaction. We also used included random intercepts for participant and random slopes for distance. The model equation was, where $outcome_{i}$ was $velocity_{i}$ or $acceleration_{i}$, and $group_{diff}$ was either $disability_{SCI}$ or $classification_{5}$, thus:

$$
\begin{aligned}
  \operatorname{outcome}_{i}  &\sim N \left(\mu, \sigma^2 \right) \\
    \mu &=\alpha_{j[i]} + \beta_{1j[i]}(\operatorname{distance}_{\operatorname{5-10m}}) + \beta_{2j[i]}(\operatorname{distance}_{\operatorname{10-15m}}) + \beta_{3j[i]}(\operatorname{distance}_{\operatorname{15-20m}}) \\    
\left(
  \begin{array}{c} 
    \begin{aligned}
      &\alpha_{j} \\
      &\beta_{1j} \\
      &\beta_{2j} \\
      &\beta_{3j}
    \end{aligned}
  \end{array}
\right)
  &\sim N \left(
\left(
  \begin{array}{c} 
    \begin{aligned}
      &\gamma_{0}^{\alpha} + \gamma_{1}^{\alpha}(\operatorname{group}_{\operatorname{diff}}) \\
      &\gamma^{\beta_{1}}_{0} + \gamma^{\beta_{1}}_{1}(\operatorname{group}_{\operatorname{diff}}) \\
      &\gamma^{\beta_{2}}_{0} + \gamma^{\beta_{2}}_{1}(\operatorname{group}_{\operatorname{diff}}) \\
      &\gamma^{\beta_{3}}_{0} + \gamma^{\beta_{3}}_{1}(\operatorname{group}_{\operatorname{diff}})
    \end{aligned}
  \end{array}
\right)
, 
\left(
  \begin{array}{cccc}
     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\beta_{1j}} & \rho_{\alpha_{j}\beta_{2j}} & \rho_{\alpha_{j}\beta_{3j}} \\ 
     \rho_{\beta_{1j}\alpha_{j}} & \sigma^2_{\beta_{1j}} & \rho_{\beta_{1j}\beta_{2j}} & \rho_{\beta_{1j}\beta_{3j}} \\ 
     \rho_{\beta_{2j}\alpha_{j}} & \rho_{\beta_{2j}\beta_{1j}} & \sigma^2_{\beta_{2j}} & \rho_{\beta_{2j}\beta_{3j}} \\ 
     \rho_{\beta_{3j}\alpha_{j}} & \rho_{\beta_{3j}\beta_{1j}} & \rho_{\beta_{3j}\beta_{2j}} & \sigma^2_{\beta_{3j}}
  \end{array}
\right)
 \right)
    \text{, for id j = 1,} \dots \text{,J}
\end{aligned}
$$


## Repeated sprint trial outcomes

For the sprint trials we examined both the time in seconds for each of the 5m sections of the 20m sprint as dependent variables in separate models. Data was handled in long format with each row corresponding to an observation of a participants time for a 5m section for a given sprint number. We fit separate models with fixed effects for either disability or classification, and in each also included a fixed effect for the distance (i.e., section of the 20m sprint trial: 0-5m, 5-10m, 10-15m, 15-20m) and also for the sprint number (from first to tenth), in addition to their interactions. We also used included random intercepts for participant and random slopes for both distance and sprint number. The model equation was, where $group_{diff}$ was either $disability_{SCI}$ or $classification_{5}$, thus:

$$
\begin{aligned}
  \operatorname{time}_{i}  &\sim N \left(\mu, \sigma^2 \right) \\
    \mu &=\alpha_{j[i]} + \beta_{1j[i]}(\operatorname{sprint\_number}) + \beta_{2j[i]}(\operatorname{distance}_{\operatorname{5-10m}}) + \beta_{3j[i]}(\operatorname{distance}_{\operatorname{10-15m}}) + \beta_{4j[i]}(\operatorname{distance}_{\operatorname{15-20m}}) + \beta_{5}(\operatorname{distance}_{\operatorname{5-10m}} \times \operatorname{sprint\_number}) + \beta_{6}(\operatorname{distance}_{\operatorname{10-15m}} \times \operatorname{sprint\_number}) + \beta_{7}(\operatorname{distance}_{\operatorname{15-20m}} \times \operatorname{sprint\_number}) \\    
\left(
  \begin{array}{c} 
    \begin{aligned}
      &\alpha_{j} \\
      &\beta_{1j} \\
      &\beta_{2j} \\
      &\beta_{3j} \\
      &\beta_{4j}
    \end{aligned}
  \end{array}
\right)
  &\sim N \left(
\left(
  \begin{array}{c} 
    \begin{aligned}
      &\gamma_{0}^{\alpha} + \gamma_{1}^{\alpha}(\operatorname{group}_{\operatorname{diff}}) \\
      &\gamma^{\beta_{1}}_{0} + \gamma^{\beta_{1}}_{1}(\operatorname{group}_{\operatorname{diff}}) \\
      &\gamma^{\beta_{2}}_{0} + \gamma^{\beta_{2}}_{1}(\operatorname{group}_{\operatorname{diff}}) + \gamma^{\beta_{2}}_{2}(\operatorname{group}_{\operatorname{diff}} \times \operatorname{sprint\_number}) \\
      &\gamma^{\beta_{3}}_{0} + \gamma^{\beta_{3}}_{2}(\operatorname{group}_{\operatorname{diff}}) + \gamma^{\beta_{3}}_{1}(\operatorname{group}_{\operatorname{diff}} \times \operatorname{sprint\_number}) \\
      &\gamma^{\beta_{4}}_{0} + \gamma^{\beta_{4}}_{1}(\operatorname{group}_{\operatorname{diff}}) + \gamma^{\beta_{4}}_{2}(\operatorname{group}_{\operatorname{diff}} \times \operatorname{sprint\_number})
    \end{aligned}
  \end{array}
\right)
, 
\left(
  \begin{array}{ccccc}
     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\beta_{1j}} & \rho_{\alpha_{j}\beta_{2j}} & \rho_{\alpha_{j}\beta_{3j}} & \rho_{\alpha_{j}\beta_{4j}} \\ 
     \rho_{\beta_{1j}\alpha_{j}} & \sigma^2_{\beta_{1j}} & \rho_{\beta_{1j}\beta_{2j}} & \rho_{\beta_{1j}\beta_{3j}} & \rho_{\beta_{1j}\beta_{4j}} \\ 
     \rho_{\beta_{2j}\alpha_{j}} & \rho_{\beta_{2j}\beta_{1j}} & \sigma^2_{\beta_{2j}} & \rho_{\beta_{2j}\beta_{3j}} & \rho_{\beta_{2j}\beta_{4j}} \\ 
     \rho_{\beta_{3j}\alpha_{j}} & \rho_{\beta_{3j}\beta_{1j}} & \rho_{\beta_{3j}\beta_{2j}} & \sigma^2_{\beta_{3j}} & \rho_{\beta_{3j}\beta_{4j}} \\ 
     \rho_{\beta_{4j}\alpha_{j}} & \rho_{\beta_{4j}\beta_{1j}} & \rho_{\beta_{4j}\beta_{2j}} & \rho_{\beta_{4j}\beta_{3j}} & \sigma^2_{\beta_{4j}}
  \end{array}
\right)
 \right)
    \text{, for id j = 1,} \dots \text{,J}
\end{aligned}
$$

# Results
```{r} 
#| message: false
#| warning: false
#| echo: false

targets::tar_load(tidy_disability_velocity_model)
targets::tar_load(tidy_classif_velocity_model)
targets::tar_load(tidy_disability_acceleration_model)
targets::tar_load(tidy_classif_acceleration_model)

disability_tab <- left_join(tidy_disability_velocity_model, tidy_disability_acceleration_model,
                          by = c("effect", "term")) %>%
  select(term, estimate.x, conf.low.x, conf.high.x, estimate.y, conf.low.y, conf.high.y)

classif_tab <- left_join(tidy_classif_velocity_model, tidy_classif_acceleration_model,
                            by = c("effect", "term")) %>%
  select(term, estimate.x, conf.low.x, conf.high.x, estimate.y, conf.low.y, conf.high.y)


tidy_model_sprint <- rbind(disability_tab, classif_tab) %>%
  mutate_if(is.numeric, round, 2)


tidy_model_sprint$term <- recode(tidy_model_sprint$term,
                              "(Intercept)" = "Intercept",
                              "disabilitySCI" = "$Disability_{SCI}$",
                              "distance5M10m" = "$Distance_{5-10m}$",
                              "distance10M15m" = "$Distance_{10-15m}$",
                              "distance15M20m" = "$Distance_{15-20m}$",
                              "disabilitySCI:distance5M10m" = "$Disability_{SCI}$:$Distance_{5-10m}$",
                              "disabilitySCI:distance10M15m" = "$Disability_{SCI}$:$Distance_{10-15m}$",
                              "disabilitySCI:distance15M20m" = "$Disability_{SCI}$:$Distance_{15-20m}$",
                              "sd__(Intercept)" = "$\\sigma_{Intercept}$",  
                              "sd__distance5M10m" = "$\\sigma_{distance5M10m}$",
                              "sd__distance10M15m" = "$\\sigma_{distance10M15m}$",
                              "sd__distance15M20m" = "$\\sigma_{distance15M20m}$",
                              "cor__(Intercept).distance5M10m" = "$\\rho_{Intercept:Distance_{5-10m}}$",
                              "cor__(Intercept).distance10M15m" = "$\\rho_{Intercept:Distance_{10-15m}}$",
                              "cor__(Intercept).distance15M20m" = "$\\rho_{Intercept:Distance_{15-20m}}$",
                              "cor__distance5M10m.distance10M15m" = "$\\rho_{Distance_{5-10m}:Distance_{10-15m}}$",
                              "cor__distance5M10m.distance15M20m" = "$\\rho_{Distance_{5-10m}:Distance_{15-20m}}$",
                              "cor__distance10M15m.distance15M20m" = "$\\rho_{Distance_{10-15m}:Distance_{15-20m}}$",
                              "sd__Observation" = "$\\sigma_{Residual}$",
                              
                              "classif5" = "$Classification_{5}$",
                              "classif5:distance5M10m" = "$Classification_{5}$:$Distance_{5-10m}$",
                              "classif5:distance10M15m" = "$Classification_{5}$:$Distance_{10-15m}$",
                              "classif5:distance15M20m" = "$Classification_{5}$:$Distance_{15-20m}$"
                              )

tidy_model_sprint <- tidy_model_sprint[c(1:14,16,15,17:33,35,35,36:38),]
```

## Sprint trial outcomes

The overall grand means and credible intervals from the models for the fixed effects (i.e., without including the random effects) for both velocity and acceleration can be seen in @fig-velocity-model-plot and @fig-acceleration-model-plot, in addition to individual data, respectively for both disability and classification models. All parameters for both outcomes and both disability and classification models are also shown in @tbl-sprint-model.

```{r} 
#| message: false
#| warning: false
#| echo: false
#| label: tbl-sprint-model 
#| tbl-cap-location: "top"
#| tbl-cap: Model parameter estimates for both fixed and random effects for sprint trial outcomes (velocity and acceleration).


knitr::kable(
  tidy_model_sprint,
  align = c("l","c","c","c","c","c","c"),
  col.names = c("Model Term",
                "Estimate",
                "Lower 95% CI",
                "Upper 95% CI",
                "Estimate",
                "Lower 95% CI",
                "Upper 95% CI"
                )
) %>%
  footnote(general = c("CI = credible interval")
           ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_classic(full_width = FALSE) %>%
  add_header_above(c(" ", "Velocity $\\\\(m\U00B7s^{-1})$" = 3, "Acceleration $\\\\(m\U00B7s^{-2})$" = 3), 
                   escape = FALSE) %>%
  pack_rows("Disability Model", 1,19) %>%
  pack_rows("Fixed Effects", 1,8, italic = TRUE, bold = FALSE) %>%
  pack_rows("Random Effects", 9,19, italic = TRUE, bold = FALSE) %>%
  pack_rows("Classification Model", 20,38) %>%
  pack_rows("Fixed Effects", 20,27, italic = TRUE, bold = FALSE) %>%
  pack_rows("Random Effects", 28,38, italic = TRUE, bold = FALSE) %>%
  kableExtra::kable_styling()

```



```{r fig-velocity-model-plot, message=FALSE, warning=FALSE, echo=FALSE, fig.height=7.5, fig.width=15, fig.cap="Individual data (top row) and global grand means with distribution and 95% credible interval estimates from the expectation of the posterior predictive distribution (bottom row) for velocity by both disability, panels (A) and (B), and classification, panels (C) and (D)."}

targets::tar_load(combined_velocity_plot)

combined_velocity_plot

```
```{r fig-acceleration-model-plot, message=FALSE, warning=FALSE, echo=FALSE, fig.height=7.5, fig.width=15, fig.cap="Individual data (top row) and global grand means with distribution and 95% credible interval estimates from the expectation of the posterior predictive distribution (bottom row) for acceleration by both disability, panels (A) and (B), and classification, panels (C) and (D)."}

targets::tar_load(combined_acceleration_plot)

combined_acceleration_plot

```

## Repeated sprint trial outcomes

# References
